--- 
title: "Introduction to Machine Learning"
date: '`r format(Sys.Date(), "%d %B %Y")`'
author: "[Chris Yeomans](mailto:c.m.yeomans@exeter.ac.uk) and Jiangjiao Xu"
site: bookdown::bookdown_site
output:
    bookdown::gitbook:
        config:
            sharing: null
        css: '_style.css'
        includes:
            in_header: '_toggle.html'
        keep_md: TRUE
        highlight: pygments
    bookdown::pdf_book:
        keep_tex: yes
        includes:
            in_header: '_header.tex'
documentclass: book
link-citations: yes
description: "Introduction to Machine Learning"
---

# Preface {-}

```{r setup, include=FALSE}
# Setup Python environment
library(reticulate)
use_python('anaconda3/bin/python3.7')
knitr::opts_chunk$set(echo=TRUE, comment=NA)
```

```{r, child="_setup.Rmd", include=F, purl=F, cache=F}
```

*This course is based on original material by JJ Valetta from Easter 2019*

An introductory workshop on the field of machine learning. The focus will be on how to use these methods
in practice using R and Python, rather than on the rigorous underlying mathematics. The target audience
is anyone who wants to know what machine learning is, what problems it can solve and how we can solve them
in practice using R or Python.

## Prerequisites {-}

* Programming basics in either R or Python

## Learning outcomes {-}

* Understand the key concepts and terminology used in the field of machine learning
* Build predictive models for clustering, regression and classification problems
* Apply machine learning algorithms in R/Python to a variety of real-world datasets
* Recognise practical issues in data-driven modelling

## Recommended reading {-}

I highly recommend the following books:

* [An Introduction to Statistical Learning](http://www-bcf.usc.edu/~gareth/ISL/)
* [The Elements of Statistical Learning](https://web.stanford.edu/~hastie/ElemStatLearn/)
* [Pattern Recognition and Machine Learning](https://www.springer.com/gp/book/9780387310732)
* [Machine Learning: A Probabilistic Perspective](https://www.cs.ubc.ca/~murphyk/MLbook/)

## Software packages {-}

* R: [`caret`](http://topepo.github.io/caret/index.html)
* Python: [`scikit-learn`](https://scikit-learn.org/stable/)

**Please make sure to read the documentation of any machine learning algorithm *before* using it!**

## Data files {-}

All data files can be downloaded as a ZIP file from [here](https://exeter-data-analytics.github.io/MachineLearning/data.zip).